Rapid Bayesian position reconstruction for gravitational\nobreakdashes-wave transients

### 2015-12-21 ms.tex
Fix bad parentheses

The Laser Interferometer Gravitational Wave Observatory (\acsu{LIGO})~\cite{AdvancedLIGOHarry,AdvancedLIGO}) has just begun taking data \cite{LIGOObservingScenarios} in its ``Advanced'' configuration. The two \ac{LIGO} detectors will ultimately increase their reach in volume within the local Universe by 3 orders of magnitude as compared to their initial configurations through 2010. They form the first parts of a sensitive global gravitational-wave (\acsu{GW}) detector network, soon to be augmented by Advanced Virgo~\cite{AdvancedVirgo} and later by the Japanese KAGRA facility~\cite{LCGT,KAGRAInterferometerDesign} and \ac{LIGO}\nobreakdashes--India~\cite{LIGOIndia}.

>>>>

The Laser Interferometer Gravitational Wave Observatory (\acsu{LIGO})~\cite{AdvancedLIGOHarry,AdvancedLIGO} has just begun taking data \cite{LIGOObservingScenarios} in its ``Advanced'' configuration. The two \ac{LIGO} detectors will ultimately increase their reach in volume within the local Universe by 3 orders of magnitude as compared to their initial configurations through 2010. They form the first parts of a sensitive global gravitational-wave (\acsu{GW}) detector network, soon to be augmented by Advanced Virgo~\cite{AdvancedVirgo} and later by the Japanese KAGRA facility~\cite{LCGT,KAGRAInterferometerDesign} and \ac{LIGO}\nobreakdashes--India~\cite{LIGOIndia}.
